gratia: An R package for exploring generalized additive models

### 2024-08-05 README.Rmd
try to stop alt text being printed
indentation
indentation again
more indentation
even more indetation
fig_caption isn't an argument to github format
rebuild
The readme could benefit from a better statement of need in the overview section; #305

Graceful 'ggplot'-based graphics and utility functions for working with
generalized additive models (GAMs) fitted using the 'mgcv' package. Provides a
reimplementation of the `plot()` method for GAMs that 'mgcv' provides, as well
as 'tidyverse' compatible representations of estimated smooths.

@@

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", dependson = -2}
appraise(m1)
```

>>>>

Working with GAMs within the 'tidyverse' can be tedious and even difficult
without a good understanding of GAMs themselves and how the model is returned
by 'mgcv' and what the model objects contain. 'gratia' is designed to help with
this.

'gratia' provides 'ggplot'-based graphics and utility functions for working with
generalized additive models (GAMs) fitted using the 'mgcv' package, via a
reimplementation of the `plot()` method for GAMs that 'mgcv' provides, as well
as 'tidyverse' compatible representations of estimated smooths.

@@

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide"}
appraise(m1)
```
